An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-18 Revision/response.tex

\noindent
\textbf{Response:}

\section*{Response to Review 1}

%%%%%%%%%%%%%%%%%%%%%% W1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{Although the authors justify the synthetic attribute generation, real-world applications may involve more complex attribute semantics and correlations, which might affect generalizability.}
	\end{weakness}
}

\noindent
\textbf{Response:} Thank you for your suggestion! In real-world applications, there may indeed exist more complex semantic correlations between vectors and their associated attributes or among different attributes themselves. To better reflect such scenarios, we introduced two real-world datasets, where both vectors and attributes are derived from actual data. For example, in the YouTube dataset, the attributes include video categories and view counts, while in the WIT dataset, the attributes correspond to the language of image descriptions.

We conducted experiments on both datasets and analyzed the performance of various algorithms. Interestingly, our results indicate that using real attribute values has limited impact on the overall performance trends.

Regarding the more intricate semantic relationships—such as those between vectors and attributes, or among different attributes themselves—current hybrid search algorithms do not explicitly model or leverage such correlations. Nevertheless, our evaluation covers a range of realistic scenarios, including multi-attribute settings and diverse  distributions, to assess the generalization ability of the algorithms.

### 2025-07-18 VLDB2026/main.tex
1

		\textcolor{orange}{As shown in Figure~\ref{fig:rangeFilter_search_memory_mb}, Faiss and Milvus have the lowest peak memory usage during search. Faiss reason: Milvus reason:. WinFilter achieves the highest peak memory usage on almost all datasets. The reason is:. For the high-dimensional dataset WIT, UNIFY occupies the highest peak memory. The reason is:.}

		%Faiss和Milvus在搜索时的峰值内存最低，\textcolor{orange}{Faiss原因：Milvus原因：}。WinFilter在几乎所有数据集上取得最高的峰值内存，\textcolor{orange}{原因是：}。而对于高维数据集WIT，UNIFY占用最高的峰值内存，\textcolor{orange}{原因是：}。

>>>>

	%	\textcolor{orange}{As shown in Figure~\ref{fig:rangeFilter_search_memory_mb}, Faiss and Milvus have the lowest peak memory usage during search. Similar to attribute filtering, Faiss also has a smaller index size and no other additional memory usage, so the peak memory usage in range queries is slightly higher than the index size. Milvus reason:. WinFilter achieves the highest peak memory usage on almost all datasets. The reason is:. For the high-dimensional dataset WIT, UNIFY occupies the highest peak memory. The reason is:.}

		\textcolor{orange}{As for the Search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the Build peak memory usage trend. The algorithm needs to load the complete index into memory during search. Therefore, algorithms with high building overhead, such as WinFilter, also have high search overhead; algorithms with low building overhead, such as Faiss, also have low search overhead. For Milvus, search does not require full index loading and there is additional metadata overhead when building, so the performance is different from the trend.}
